---
title: "abobo"
author: "me"
date: "3/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("naniar")
install.packages("skimr")
library(tidyverse)
library("naniar")
library("skimr")
library(shiny)
library(shinydashboard)
```
General analysis
```{r}
AbaloneData<-readr::read_csv("AbaloneData.csv")
AbaloneData
naniar::miss_var_summary(AbaloneData)
```
show analysis (apps)
    plots/apps to show correlations with mass and through
    correlation between sex and mass
    plots/apps to show correlation to sex
    show fertility(gonad score > 0)
      (gonad score vs mass & length)
      fertility vs sex
      length vs mass filled by predicted sex
      average growth -> use to compare to other factors like sex and gonad score and trough

 average growth
```{r}
AbaloneData1<-AbaloneData %>%
  mutate(avgGrowthRate_GperMonth = Mass_g/24)
AbaloneData1
```
Mass vs Length by predicted sex shows no statistically significant evidence for a difference between sex
otherise shows somewhat logarithmic correlation between mass in grams and length in mm
```{r}
AbaloneData1%>%
  filter(Predicted_Sex == "M") %>%
  summarise(avgMassM = mean(Mass_g))
AbaloneData1%>%
  filter(Predicted_Sex == "F") %>%
  summarise(avgMassF = mean(Mass_g))
```
```{r}
AbaloneData1%>%
  filter(Predicted_Sex == "M" | Predicted_Sex == "F") %>%
  group_by(Predicted_Sex)%>%
  summarize(avgMass=mean(Mass_g))%>%
  ggplot(aes(x=Predicted_Sex, y=avgMass, color = Predicted_Sex)) +
  geom_bar(stat="identity")
```
```{r}
AbaloneData1%>%
  filter(Predicted_Sex == "M" | Predicted_Sex == "F") %>%
  group_by(Predicted_Sex)%>%
  summarize(avgGrowth=mean(avgGrowthRate_GperMonth))%>%
  ggplot(aes(x=Predicted_Sex, y=avgGrowth, color = Predicted_Sex)) +
  geom_bar(stat="identity")
```

```{r}
AbaloneData1 %>% 
  filter(Predicted_Sex == "M" | Predicted_Sex == "F") %>%
  ggplot(aes(x=Length_mm, y=Mass_g, color = Predicted_Sex)) +
  geom_jitter() + geom_smooth(se = FALSE)
```





