---
title: "white abalone"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(shiny)
library(shinydashboard)
```

```{r}
getwd()
```

```{r}
WA<- readr::read_csv("AbaloneData.csv")
```

```{r}
colnames(WA
        )
WA
```

```{r}
library("tidyverse")
library("naniar")
```


```{r}
###finding mean mass for all troughs 
WAcat1<-
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "1") 

mean(WAcat1$`Mass_(g)`, na.rm = TRUE)



WAcat1<-
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "2") 

mean(WAcat1$`Mass_(g)`, na.rm = TRUE)


WAcat1<-
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "3") 

mean(WAcat1$`Mass_(g)`, na.rm = TRUE)


WAcat1<-
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "4") 

mean(WAcat1$`Mass_(g)`, na.rm = TRUE)


```


```{r}
##finding variance of mass for all troughs
WAcat1
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "1") 

var(WAcat1$`Mass_(g)`, na.rm = TRUE)

WAcat1<-
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "2") 

var(WAcat1$`Mass_(g)`, na.rm = TRUE)

WAcat1<-
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "3") 

var(WAcat1$`Mass_(g)`, na.rm = TRUE)

WAcat1<-
WA %>% 
  filter(Growout_Column == "A" & Growout_Trough == "4") 

var(WAcat1$`Mass_(g)`, na.rm = TRUE)


```



```{r}
str(WA)
naniar::miss_var_summary(WA)
WA
```


```{r}
WA2<-
WA %>% 
  filter(Growout_Column == "A") %>% 
  select(Growout_Trough, `Mass_(g)`, Gonad_Score) 

  WA2 %>% 
    group_by(Growout_Trough) %>% 
  summarize(reproductive_individuals= sum(Gonad_Score > 0)) %>% 
    ggplot(aes(x= Growout_Trough, y= reproductive_individuals, fill= Growout_Trough))+
    geom_col()
  
WA2 %>% 
  group_by(Growout_Trough) %>% 
  summarize(reproductive_individuals= sum(Gonad_Score > 0 ))


```
```{r}

WA %>% 
  filter(Growout_Column == "A") %>% 
  select(Growout_Trough, `Length_(mm)`, `Mass_(g)`, Gonad_Score) %>% 
    group_by(Growout_Trough) %>% 
  summarise(GS_score= sum(Gonad_Score > 0 ))


WA %>% 
  filter(Growout_Column == "A") %>% 
  select(Growout_Trough, `Length_(mm)`, `Mass_(g)`, Gonad_Score) %>% 
    group_by(Growout_Trough) %>% 
  summarise(mean_mass= mean(`Mass_(g)`))


WA %>% 
  filter(Growout_Column == "A") %>% 
  select(Growout_Trough, `Length_(mm)`, `Mass_(g)`, Gonad_Score) %>% 
    group_by(Growout_Trough) %>% 
  summarise(mean_lenght= mean(`Length_(mm)`))

```
```{r}
WA2$Gonad_Score

sum(WA2$Gonad_Score > 0 )
```
```

```{r}
Trough<- c(1,2,3,4)
GCS<- c(5,9,7,14)
MM<- c(5.9272, 4.2424, 3.4080, 4.4500)
ML<- c(27.072, 26.524, 22.846, 27.868)
APP<- data_frame(Trough, GCS, MM, ML)
APP
```




```{r}
ui <- dashboardPage(
  dashboardHeader(title = "How water quality affects WA"),
  dashboardSidebar(),
  dashboardBody(
  fluidRow(
  box(title = "Plot Options", width = 3,
  selectInput("y", "Select Y Variable", choices = c("GCS", "MM", "ML"))
  ), # close the first box
  box(title = "Plot of Water quality vs sucess", width = 7,
  plotOutput("plot", width = "600px", height = "500px")
  ) # close the second box
  ) # close the row
  ) # close the dashboard body
) # close the ui

server <- function(input, output, session) { 
  
  output$plot <- renderPlot({
    ggplot(APP, aes_string(x = "Trough", y =  input$y)) + geom_col() + theme_light(base_size = 18)
  })
  
  # stop the app when we close it
  session$onSessionEnded(stopApp)

  }

shinyApp(ui, server)
```
```{r}
WA
```


```{r}
### the app made me curious about amount of data in each trough so i used this code to figure out how many observations were in each trough diferences in this will skew the data
wa2<- WA %>% 
  filter(Growout_Column == "A") 
  
  sum(wa2$Growout_Trough > 0 &wa2$Growout_Trough < 2)
sum(wa2$Growout_Trough > 1 &wa2$Growout_Trough < 3)
sum(wa2$Growout_Trough > 2 &wa2$Growout_Trough < 4)
sum(wa2$Growout_Trough > 3 &wa2$Growout_Trough < 5)

  ## i found that there was a difference in the number of observations so this will affect the count of individuals that are reoroductive so I will fix this in the app by dividing by the sample size (Like a mean)
  
```

```{r}
## so this is the new data frame: 
Trough
GCS2<- c(5/25,9/25,7/50,14/50)
MM2<- c(5.9272, 4.2424, 3.4080, 4.4500)
ML2<- c(27.072, 26.524, 22.846, 27.868)
APP2<- data_frame(Trough, GCS2, MM2, ML2)
APP2
```

```{r}
ui <- dashboardPage(
  dashboardHeader(title = "How water quality affects WA"),
  dashboardSidebar(),
  dashboardBody(
  fluidRow(
  box(title = "Plot Options", width = 3,
  selectInput("y", "Select Y Variable", choices = c("GCS2", "MM2", "ML2"))
  ), # close the first box
  box(title = "Plot of Water quality vs sucess", width = 7,
  plotOutput("plot", width = "600px", height = "500px")
  ) # close the second box
  ) # close the row
  ) # close the dashboard body
) # close the ui

server <- function(input, output, session) { 
  
  # the code to make the plot of iris data grouped by species
  output$plot <- renderPlot({
    ggplot(APP2, aes_string(x = "Trough", y =  input$y)) + geom_col() + theme_light(base_size = 18)
  })
  
  # stop the app when we close it
  session$onSessionEnded(stopApp)

  }

shinyApp(ui, server)

```














